A Formal Model of Checked C

### 2023-01-15 sandp23/implementation.tex
Adding

We created the sandbox library once and for all for each sandbox.
This library abstracts the sandbox-specific details and exposes a uniform interface (header file) to be used in~\cregion.
For instance,~\code{_SBX_()} gets an opaque pointer to the target sandbox.
We will present our implementation using WebAssembly (WASM~\cite{bosamiya2020webassembly}) as our target sandbox.
However, as we discuss in~\sect{}, our implementation can be easily extended to other sandbox mechanisms.

@@

\noindent\emph{\_Callback}:
Developers should use this qualifier to mark callback functions,~\ie functions in~\cregion, that can be called from the tainted region. 
The~\sourcerewriter inserts appropriate sandbox-dependent mechanisms to enable this (\sect{}).

>>>>

We created the sandbox library once and for all for each sandbox.
This library abstracts the sandbox-specific details and exposes a uniform interface (header file) to be used in~\cregion.
For instance,~\code{_SBX_()} gets an opaque pointer to the target sandbox.
We will present our implementation using WebAssembly (WASM~\cite{bosamiya2020webassembly}) as our target sandbox.
%However, as we discuss in~\sect{}, our implementation can be easily extended to other sandbox mechanisms.

@@

\noindent\emph{\_Callback}:
Developers should use this qualifier to mark callback functions,~\ie functions in~\cregion, that can be called from the tainted region. 
The~\sourcerewriter inserts appropriate sandbox-dependent mechanisms to enable this (\sect{subsub:gencregion}).
